Discussion

### 2025-12-02 GroupPolarizationStatmod/paper/Discussion.qmd

\newcommand{\mupre}{\mu_\mathrm{pre}}
\newcommand{\mupost}{\mu_\mathrm{post}}

\newcommand{\sigmapre}{\sigma_\mathrm{pre}}
\newcommand{\sigmapost}{\sigma_\mathrm{post}}

@@

The center of this distribution, the **posterior median ($\tilde{d}$)**, is the most robust point estimate for the effect size, as it minimizes expected absolute error and is less sensitive to potential skewness than the posterior mean.

>>>>

\newcommand{\mupre}{\mu_\mathrm{pre}}
\newcommand{\mupost}{\mu_\mathrm{post}}
\newcommand{\sigmapre}{\sigma_\mathrm{pre}}
\newcommand{\sigmapost}{\sigma_\mathrm{post}}

@@

The center of this distribution, the **posterior median (**$\tilde{d}$), is the
most robust point estimate for the effect size, as it minimizes expected
absolute error and is less sensitive to potential skewness than the posterior
mean.
